Family Fortunes: A Quantitative Analysis of the Early Iron Age Cemeteries at Knossos, Crete

### 2020-10-13 analysis/paper/Family_Fortunes_Article.Rmd
Figure edits

#The appropriate packages are installed. Extrafont allows the use of non-standard fonts in R plots, ggplot2 is a powerful figure and graph plotting tool, and RColorBrewer includes a number of colour pallettes which can be applied to plots. The colour scheme in this paper is chosen from those that are suitable for colour-blind readers. The font Garmond is installed and stored.
library(ggpubr)
library(ineq)
library(reshape)
library(data.table)
library(ggplot2)
library(RColorBrewer)
library(grid)
library(dplyr)
library(plyr)
library(ggforce)
library(png)
library(ggrepel)

@@

```{r map, out.width="50%", fig.cap="goes around here"}
knitr::include_graphics("../figures/Knossos Tombs Map2.jpg")
```

@@

```{r burialestimate, fig.dim = c(7, 7), dpi=600, fig.align='center', fig.cap="goes around here"}

#Figure 1 is plotted, with axis limits set (excluding tomb P, resulting in the warning message delivered) and the style of the plot adjusted (including font and text size, the appearance of the gridlines, selecting a colour palette etc.)

p<-ggplot(tombs)+geom_point(aes(est_burials,all_urns,color="All urns"))+
  geom_point(aes(est_burials,total_burials,color="Known interments"))+
    geom_point(aes(est_burials,pithoi,colour="Pithoi"))+
      geom_line(aes(est_burials,est_burials),alpha=0.4)+
       scale_x_continuous(expand=c(0,0),limits=c(0,55))+
        scale_y_continuous(expand=c(0,0),limits=c(0,55))+theme_bw()+
         theme(legend.title=element_blank(),
          text=element_text(family="serif", size=12),legend.position="bottom")+
              labs(x="Mean Burial Estimate", y="Interment/Vessel Count")+
                 scale_color_brewer(palette = "Set2")

#The coordinates of the plot are adjusted to render the axes equal, and the corresponding gridlines as squares, and then the figure is plotted.

p<-p+coord_fixed()
plot(p)

@@

```{r allpithoi,fig.dim = c(8, 4), dpi=600, fig.align='center', fig.cap="goes around here"}

@@

non_aorist_fig<-ggplot(pots, aes(ave_date,fill="Pots"))+geom_histogram(fill="gray40")+
  theme_bw()+theme(legend.title=element_blank(),
      text=element_text(family="serif", size=12))+
          labs(x="Date (Years BC)", y="Vessel Count")+
                theme(legend.position="none")+
                  scale_y_continuous(expand=c(0,0),limits=c(0,600))+
                    scale_x_reverse(expand = c(0, 0),limits=c(1100,600))+
                      theme(plot.margin=unit(c(0.1,1,0.1,0.1),"cm"))

@@

aorist_fig<-ggplot(aorist_all_tombs,aes(decade,aoristic_sum, fill="Aoristic Sum"))+
  geom_col(fill="gray40")+theme_bw()+theme(legend.title=element_blank(),
      text=element_text(family="serif", size=12))+
          labs(x="Date (Years BC)", y="Aoristic Sum")+
               theme(legend.position="none")+
                  scale_y_continuous(expand=c(0,0),limits=c(0,225))+
                    scale_x_reverse(expand = c(0, 0),limits=c(1100,600))+
                      theme(plot.margin=unit(c(0.1,1,0.1,0.1),"cm"))

@@

```{r aoristbycem, dpi=600, fig.align="center", fig.cap="goesaround here.", fig.dim=c(8,4)}
KNC<-subset(tombs,tombs$cem_condensed=="KNC")

@@

aorist_pithoi_plot<-ggplot(NULL)+
  geom_col(data=aorist_all_pithoi,aes(decade,aoristic_sum,fill=" All tombs  "))+
    geom_col(data=aorist_KNC_pithoi,aes(decade,aoristic_sum,fill=" KNC  "))+
      geom_col(data=aorist_FOR_pithoi,aes(decade,aoristic_sum, fill=" Fortetsa  "))+
        theme_bw()+theme(legend.title=element_blank(),
          text=element_text(family="serif", size=12))+
            labs(x="Date (Years BC)", y="Aoristic Sum (Pithoi)")+
              scale_fill_manual(values = c("gray50","gray65","gray80"))+ 
                  scale_y_continuous(expand=c(0,0),limits=c(0,45))+
                    scale_x_reverse(expand = c(0, 0),limits=c(1100,600))+
                      theme(plot.margin=unit(c(0.1,1,0.1,0.1),"cm"))

@@

aorist_pots_plot<-ggplot(NULL)+
  geom_col(data=aorist_all_tombs,aes(decade,aoristic_sum,fill=" All tombs  "))+
    geom_col(data=aorist_KNC,aes(decade,aoristic_sum,fill=" KNC  "))+
      geom_col(data=aorist_FOR,aes(decade,aoristic_sum, fill=" Fortetsa  "))+
        theme_bw()+theme(legend.title=element_blank(),
          text=element_text(family="serif", size=12))+
            labs(x="Date (Years BC)", y="Aoristic Sum (All Vessels)")+
              scale_fill_manual(values = c("gray50","gray65","gray80"))+  
                  scale_y_continuous(expand=c(0,0),limits=c(0,225))+
                    scale_x_reverse(expand = c(0, 0),limits=c(1100,600))+
                      theme(plot.margin=unit(c(0.1,1,0.1,0.1),"cm"))

@@

```{r tombsinuse, fig.dim=c(7,7), dpi=600, fig.cap="goes around here"}

@@

ggplot(tombs_in_use_cem,aes(period,no_tombs, fill=cemetery))+geom_col(position="dodge")+theme_classic()+
       theme_bw()+theme(legend.title=element_blank(),
          text=element_text(family="serif", size=12),legend.position = "bottom")+
            labs(x="Period", y="Tombs in Use")+
              scale_fill_manual(values =c("gray50","gray80"),labels=c(" KNC  "," Fortetsa"))+ 
                 scale_y_continuous(expand=c(0,0),limits=c(0,45))
```

@@

```{r potsbydateandtombdate,  fig.dim=c(7,14), dpi=600, fig.cap="goes around here"}

@@

date_by_vessel<-ggplot(data=subset(pots,pots$century!=""),aes(century,fill="Date"))+geom_bar()+
  theme_bw()+theme(legend.position="none",
               text=element_text(family="serif", size=12))+
                 labs(x="Century BC (Date of Vessel)", y="Vessel Count")+
                  scale_fill_manual(values = c("gray50"))+ 
                    scale_y_continuous(expand=c(0,0),limits=c(0,2800))

date_by_tomb<-ggplot(data=subset(pots,pots$century!=""),aes(tomb_century,fill="Date"))+geom_bar()+
  theme_bw()+theme(legend.position="none",
               text=element_text(family="serif", size=12))+
                 labs(x="Century BC (Date of Tomb)", y="Vessel Count")+
                  scale_fill_manual(values = c("gray50"))+ 
                    scale_y_continuous(expand=c(0,0),limits=c(0,2800))

@@

```{r dimensionsboxplots, fig.dim=c(7,6),dpi=600, fig.align='center',fig.cap="goes around here"}

@@

```{r tombgroupdimensions, fig.dim = c(7, 6), dpi=600, fig.align='center', fig.cap="goes around here"}

ggplot(subset(tombs,century_built=="9th" | century_built=="10th"),aes(dromos_length,chamber_area,color=group,label=tomb))+geom_point()+
  theme_bw()+theme(text=element_text(family="serif", size=10),legend.position = "bottom")+
  geom_label_repel(data=subset(tombs,group!="C"),aes(fill=group),color="white",show.legend = FALSE,family="serif")+
            labs(x="Dromos Length (m)", y="Chamber Area (sq m)")+
               scale_color_brewer(palette = "Set2",name="Group")+
               scale_fill_brewer(palette = "Set2")+
                scale_x_continuous(expand=c(0,0),limits=c(0,10))+
                  scale_y_continuous(expand=c(0,0),limits=c(0,10))+
                      theme(plot.margin=unit(c(0.1,1,0.1,0.1),"cm"))+coord_fixed()

>>>>

#The appropriate packages are installed. Extrafont allows the use of non-standard fonts in R plots, ggplot2 is a powerful figure and graph plotting tool, and RColorBrewer includes a number of colour pallettes which can be applied to plots. The colour scheme in this paper is chosen from those that are suitable for colour-blind readers.
library(ggpubr)
library(ineq)
library(reshape)
library(data.table)
library(ggplot2)
library(RColorBrewer)
library(grid)
library(dplyr)
library(plyr)
library(ggforce)
library(jpeg)
library(ggrepel)

@@

```{r map, fig.align= "centre", fig.cap="goes around here"}

knitr::include_graphics("../figures/Knossos Tombs Map2.jpg")
```

@@

@@

```{r allpithoi,fig.dim = c(8, 3), dpi=600, fig.align='center', fig.cap="goes around here"}

@@

non_aorist_fig<-ggplot(pots, aes(ave_date,fill="Pots"))+geom_histogram(fill="gray40")+
  theme_bw()+theme(legend.title=element_blank(),
      text=element_text(family="serif", size=11))+
          labs(x="Date (Years BC)", y="Vessel Count")+
                theme(legend.position="none")+
                  scale_y_continuous(expand=c(0,0),limits=c(0,610))+
                    scale_x_reverse(expand = c(0, 0),limits=c(1100,600))+
                      theme(plot.margin=unit(c(0.1,1,0.1,0.1),"cm"))

@@

aorist_fig<-ggplot(aorist_all_tombs,aes(decade,aoristic_sum, fill="Aoristic Sum"))+
  geom_col(fill="gray40")+theme_bw()+theme(legend.title=element_blank(),
      text=element_text(family="serif", size=11))+
          labs(x="Date (Years BC)", y="Aoristic Sum")+
               theme(legend.position="none")+
                  scale_y_continuous(expand=c(0,0),limits=c(0,225))+
                    scale_x_reverse(expand = c(0, 0),limits=c(1100,600))+
                      theme(plot.margin=unit(c(0.1,1,0.1,0.1),"cm"))

@@

```{r aoristbycem, dpi=600, fig.align="center", fig.cap="goesaround here.", fig.dim=c(8,3.5)}
KNC<-subset(tombs,tombs$cem_condensed=="KNC")

@@

aorist_pithoi_plot<-ggplot(NULL)+
  geom_col(data=aorist_all_pithoi,aes(decade,aoristic_sum,fill=" All tombs  "))+
    geom_col(data=aorist_KNC_pithoi,aes(decade,aoristic_sum,fill=" KNC  "))+
      geom_col(data=aorist_FOR_pithoi,aes(decade,aoristic_sum, fill=" Fortetsa  "))+
        theme_bw()+theme(legend.title=element_blank(),
          text=element_text(family="serif", size=11))+
            labs(x="Date (Years BC)", y="Aoristic Sum (Pithoi)")+
              scale_fill_manual(values = c("gray50","gray65","gray80"))+ 
                  scale_y_continuous(expand=c(0,0),limits=c(0,45))+
                    scale_x_reverse(expand = c(0, 0),limits=c(1100,600))+
                      theme(plot.margin=unit(c(0.1,1,0.1,0.1),"cm"))

@@

aorist_pots_plot<-ggplot(NULL)+
  geom_col(data=aorist_all_tombs,aes(decade,aoristic_sum,fill=" All tombs  "))+
    geom_col(data=aorist_KNC,aes(decade,aoristic_sum,fill=" KNC  "))+
      geom_col(data=aorist_FOR,aes(decade,aoristic_sum, fill=" Fortetsa  "))+
        theme_bw()+theme(legend.title=element_blank(),
          text=element_text(family="serif", size=11))+
            labs(x="Date (Years BC)", y="Aoristic Sum (All Vessels)")+
              scale_fill_manual(values = c("gray50","gray65","gray80"))+  
                  scale_y_continuous(expand=c(0,0),limits=c(0,225))+
                    scale_x_reverse(expand = c(0, 0),limits=c(1100,600))+
                      theme(plot.margin=unit(c(0.1,1,0.1,0.1),"cm"))

@@

```{r tombsinuse, fig.dim=c(3,3),out.width="25%", dpi=600, fig.cap="goes around here"}

@@

ggplot(tombs_in_use_cem,aes(period,no_tombs, fill=cemetery))+geom_col(position="dodge")+theme_classic()+
       theme_bw()+theme(legend.title=element_blank(),
          text=element_text(family="serif", size=10),legend.position = "bottom")+
            labs(x="Period", y="Tombs in Use")+
              scale_fill_manual(values =c("gray50","gray80"),labels=c(" KNC  "," Fortetsa"))+ 
                 scale_y_continuous(expand=c(0,0),limits=c(0,45))
```

@@

```{r potsbydateandtombdate,  fig.dim=c(3,7),out.width="0.5%", dpi=600, fig.cap="goes around here"}

@@

date_by_vessel<-ggplot(data=subset(pots,pots$century!=""),aes(century,fill="Date"))+geom_bar()+
  theme_bw()+theme(legend.position="none",
               text=element_text(family="serif", size=10),axis.text.y=element_text(angle=90, vjust=0, hjust=0.5))+
                 labs(x="Century BC (Date of Vessel)", y="Vessel Count")+
                  scale_fill_manual(values = c("gray50"))+ 
                    scale_y_continuous(expand=c(0,0),limits=c(0,2800))

date_by_tomb<-ggplot(data=subset(pots,pots$century!=""),aes(tomb_century,fill="Date"))+geom_bar()+
  theme_bw()+theme(legend.position="none",
               text=element_text(family="serif", size=10),axis.text.y=element_text(angle=90, vjust=0, hjust=0.5))+
                 labs(x="Century BC (Date of Tomb)", y="Vessel Count")+
                  scale_fill_manual(values = c("gray50"))+ 
                    scale_y_continuous(expand=c(0,0),limits=c(0,2800))

@@

```{r dimensionsboxplots, fig.dim=c(7,7),dpi=600, fig.align='center',fig.cap="goes around here"}

@@

```{r tombgroupdimensions, fig.dim = c(3.5, 3.5),out.width="10%", dpi=600, fig.align='center', fig.cap="goes around here"}

ggplot(subset(tombs,century_built=="9th" | century_built=="10th"),aes(dromos_length,chamber_area,color=group,label=tomb))+geom_point(size=1)+
  theme_bw()+theme(text=element_text(family="serif", size=10),legend.position = "bottom", legend.margin=margin(0,0,0,0),legend.box.margin=margin(-10,-10,-10,-10))+
  geom_label_repel(data=subset(tombs,group!="C"),aes(fill=group),color="white",show.legend = FALSE,family="serif")+
            labs(x="Dromos Length (m)", y="Chamber Area (sq m)")+
               scale_color_brewer(palette = "Set2",name="Group")+
               scale_fill_brewer(palette = "Set2")+
                scale_x_continuous(expand=c(0,0),limits=c(0,8))+
                  scale_y_continuous(expand=c(0,0),limits=c(0,10))+
                      theme(plot.margin=unit(c(0.1,1,0.1,0.1),"cm"))
